Revealing Benefits, Costs, and Tradeoffs of Spatial Management Arrising from Coupled Economic and Ecological Dynamics in Marine Systems

### 2023-03-30 README.Rmd
prepping for edits on squid
Final steps (#8)
* final model runs with updated CTMC parameterization and Lorenzen mortality
---------

Co-authored-by: dovando_iattc <danovan@iattc.org>

4. In the terminal, run `RUN_NAME:MyRunName FORMAT:MyFormat make` where MyRunName is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, or docx

5. Wait for a bit! This command will run all the required scripts and knit the paper. Should take no more than a few hours.

>>>>

4. In the terminal, run `RUN_NAME="MyRunName" FORMAT="MyFormat" make` where MyRunName is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, or docx

5. Wait for a bit! This command will run all the required scripts and knit the paper. Shouldn't take more than an hour on a reasonable computer with parallel computation capabilities.
